---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Track numerical optimization

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/trackopt)](https://CRAN.R-project.org/package=trackopt)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/grand-total/trackopt)](https://CRAN.R-project.org/package=trackopt)
[![R-CMD-check](https://github.com/loelschlaeger/trackopt/workflows/R-CMD-check/badge.svg)](https://github.com/loelschlaeger/trackopt/actions)
[![Codecov test coverage](https://codecov.io/gh/loelschlaeger/trackopt/branch/main/graph/badge.svg)](https://app.codecov.io/gh/loelschlaeger/trackopt?branch=main)
<!-- badges: end -->

The `{trackopt}` package tracks parameter values, gradients, and Hessians at each iteration  of numerical optimizers in `R`. This can be useful for analyzing optimization progress, diagnosing issues, and studying convergence behavior.

## Installation

You can install the released package version from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("trackopt")
```

## Example

The following is the `nlm` minimization track of the [Himmelblau's function](https://en.wikipedia.org/wiki/Himmelblau%27s_function):

```{r himmelblau, message = FALSE}
library("trackopt")
himmelblau <- function(x) (x[1]^2 + x[2] - 11)^2 + (x[1] + x[2]^2 - 7)^2
track <- nlm_track(f = himmelblau, p = c(0, 0))
print(track)
summary(track)
ggplot2::autoplot(track)
```

The following is the `optim` maximization track of the [Beta-PDF](https://en.wikipedia.org/wiki/Beta_distribution):

```{r beta, message = FALSE}
optim_track(
  f = dbeta, p = 0, lower = 0, upper = 1, shape1 = 4, shape2 = 2, method = "Brent", minimize = FALSE
) |> ggplot2::autoplot()
```

## Contact

If you have any questions, found a bug, need a feature, [just file an issue on GitHub](https://github.com/loelschlaeger/trackopt/issues/new/choose). 
